### 2015-03-01 docs/report/micro_benchmarks.tex
Notes about benchmarks

Alternatively it could notice that the variable \code{j} is not being used so it could just throw the line away. In any case, we would just be measuring how long it takes for JavaScript to execute the loop, which is not what we originally intended to do. To verify that is not the case the tool IRHydra\cite{ir-hydra} can be used , which \textit{can display intermediate representations used by V8}. As shown in the following figure, v8 inline the function (the blue chevron marks that) but the loop invariant was not detected and optimized:
\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{naive_benchmark_ir_hydra}
  \caption{Optimized benchmark code with inlined function.}
\end{figure}
\pagebreak

>>>>

Alternatively it could notice that the variable \code{j} is not being used so it could just throw the line away. In any case, we would just be measuring how long it takes for JavaScript to execute the loop, which is not what we originally intended to do. To verify that is not the case the tool IRHydra\cite{ir-hydra} can be used , which \textit{can display intermediate representations used by V8}. As shown in the following figure, v8 inline the function (the blue chevron marks that) but the loop invariant was not detected and optimized:
\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{naive_benchmark_ir_hydra}
  \caption{Optimized benchmark code with inlined function.}
\end{figure}

\note{All benchmarks are performed using two different versions of Google Chrome (40.0.2214 and 41.0.2272) to be able to get an idea of the evolution of each feature.}

\note{Each benchmark is executed 5 (five) times to reduce variance.}

\note{No browser plug-ins are enabled when running the benchmarks as those could introduce additional sources of error.}
\pagebreak
